Using spatially biased variables in ecosystem condition accounting with a GIS based workflow

### 2024-01-29 manuscript/HIAs.qmd
calculate km distance

@@

We chose three municipalities in Norway to test out the indicators (@fig-studyLocation).
These municipalities are spread over `r round(max(latlong$Y)-min(latlong$Y), 1)` degrees latitude, and also differ in the amount of mire area, the total area surveyed, and the prevalence of infrastructure (@tbl-variables).

>>>>

km_distance <- centroids |>
  st_distance() |>
  max() |>
  set_units("km") |>
  drop_units() |>
  round()

@@

We chose three municipalities in Norway to test out the indicators (@fig-studyLocation).
These municipalities are spread over `r round(max(latlong$Y)-min(latlong$Y), 1)` degrees latitude, or `r km_distance` km, and also differ in the amount of mire area, the total area surveyed, and the prevalence of infrastructure (@tbl-variables).
